---
title: "WGCNA"
author: "Cox Lab"
execute: 
  eval: false
format: 
  html:
    toc: true
    toc-depth: 4
    toc-expand: false
    number-sections: true
    number-depth: 4
editor: source
date: today
bibliography: references.bib
csl: nature.csl
---

## Weighted Gene Co-expression Network Analysis

This package is provided through the R-language integration into Perseus and therefore requires R as well as the package itself to be installed in order to be used. Visit the [PluginInterop](https://github.com/jdrudolph/PluginInterop) and [PerseusR](https://github.com/jdrudolph/PerseusR) for additional technical information on the integration of R and Perseus.

## Installation

  * Download the R installer install it.
  * Remember the R installation directory. If you do not know where you have installed R, check the default location `C:\Program Files\R\R-3.5.0\bin`, or search for `Rscript.exe`.
  * Add R to your `Path` environment variable. Open the start menu and search for "environment variables", and select "Edit system environment variables".
  * Find the `Path` variable in the editor and select `Edit`.
  * Now we can add R to the `Path` by clicking `New` and entering the location of the `.../bin` folder of the R installation, e.g `C:\Program Files\R\R-3.5.0\bin`.
  * In certain Windows version you might have to edit the `Path` directly. The `Path` consists of folder locations separated by ‘;’. Therefore, just append the installation location of R and the ‘;’ separator. No spaces or quotes are required. If the `Path` variable is not defined on your system, you can define it yourself.
  * Check that R is installed correctly by opening `cmd.exe` from the start menu and entering `R` An R session should start.
  * Inside the running R session, install the [WGCNA](https://cran.r-project.org/web/packages/WGCNA/index.html) and [PerseusR](https://github.com/jdrudolph/PerseusR) libraries by entering/pasting the following code **line-by-line**. 
  When prompted for local install, type ‘yes’ twice and select a close-by server for the package download. 
```{r}
# | eval: false
install.packages("BiocManager")
BiocManager::install(c("WGCNA", "devtools"))
library(devtools)
install_github('jdrudolph/PerseusR')
```
  * You should now be able to load the `WGCNA` and `PerseusR` libraries by entering the following code. Upon loading, `WGCNA` will print some output, while `PerseusR` will not print any.
```{r}
# | eval: false
library(WGCNA)
library(PerseusR)
```

You are now ready to perform co-expression analysis from within Perseus.

## WGCNA functions

* [Soft-threshold](docs/softthreshold.html)
* [Co-expression clustering](docs/coexpressionclustering.html)
